Enzo+Moray: Radiation Hydrodynamics Adaptive Mesh Refinement Simulations with Adaptive Ray Tracing

### 2011-02-08 mnras/mnras.tex
Finished responding to referee report.

We have structured this paper as follows.  In Section 2, we describe
the mathematical connections between adaptive ray tracing and the
radiative transfer equation.  Furthermore, we detail how physics other
than photo-ionisation and photo-heated are included.  We then derive a
geometric correction factor to any ray tracing method to improve
accuracy.  We end the section by describing a new computational
technique to approximate an optically-thin radiation field with ray
tracing and multiple sources.  In Section 3, we cover the details of
our radiation hydrodynamics implementation in \enzo, specifically (1)
the ray tracing algorithms, (2) coupling with the hydrodynamics
solver, (3) several methods to calculate the radiative transfer
timestep, and (4) our parallelisation strategy.  We present our
results from the RT06 radiative transfer tests in Section 4.
Afterwards in Section 5, we show the results from the RT09 radiation
hydrodynamics tests.  In Section 6, we expand on these tests to
include more dynamical and complex setups to demonstrate the
flexibility and high fidelity of \moray.  Section 7 gives the results
from spatial, angular, frequency, and temporal resolution tests.  In
Section 8, we illustrate the improvements from the geometric
correction factor and our optically-thin approximation.  We also show
the effects of X-ray radiation and radiation pressure in this section.
Finally in Section 9, we demonstrate the parallel scalability of
\moray.  Last Section 10 summarises our method and results.

@@

We next show results from radiation hydrodynamics test problems
presented in \citet[][hereafter RT09]{Iliev09}.  They involve (1) the
expansion of an \hii region in a uniform medium, similar to Test
2, (2) an \hii region in an isothermal sphere, and (3) the
photo-evaporation of a dense, cold clump, similar to Test 3.  We
expand on this test suite to include more complex situations, such as
a Rayleigh-Taylor problem illuminated by a radiation source, champagne
flows, an irradiated blast wave, collimated radiation, and an
\hii with a variable source.  For the \citeauthor{Iliev09}
tests, we turn off self-gravity and AMR in accordance with them.  In
the latter tests, we will indicate whether we use those capabilities
of \enzo.  Last we use the new MHD implementation in \enzo~v2.0 in the
problem of a growing \hii region in a magnetic field.

@@

We have completed presenting results from the RT06 and RT09 test
suites.  Next we test \moray~with six applications that further
demonstrate its capabilities and accuracy.

>>>>

We have structured this paper as follows.  In Section 2, we describe
the mathematical connections between adaptive ray tracing and the
radiative transfer equation.  Furthermore, we detail how physics other
than photo-ionisation and photo-heating are included.  We then derive a
geometric correction factor to any ray tracing method to improve
accuracy.  We end the section by describing a new computational
technique to approximate an optically-thin radiation field with ray
tracing and multiple sources.  In Section 3, we cover the details of
our radiation hydrodynamics implementation in \enzo, specifically (1)
the ray tracing algorithms, (2) coupling with the hydrodynamics
solver, (3) several methods to calculate the radiative transfer
timestep, and (4) our parallelisation strategy.  We present our
results from the RT06 radiative transfer tests in Section 4.
Afterwards in Section 5, we show the results from the RT09 radiation
hydrodynamics tests.  In Section 6, we expand on these tests to
include more dynamical and complex setups to demonstrate the
flexibility and high fidelity of \moray.  Section 7 gives the results
from spatial, angular, frequency, and temporal resolution tests.  In
Section 8, we illustrate the improvements from the geometric
correction factor and our optically-thin approximation.  We also show
the effects of X-ray radiation and radiation pressure in this section.
Finally in Section 9, we demonstrate the parallel scalability of
\moray.  Last Section 10 summarises our method and results.

@@

We next show results from radiation hydrodynamics test problems
presented in \citet[][hereafter RT09]{Iliev09}.  They involve (1) the
expansion of an \hii region in a uniform medium, similar to Test 2,
(2) an \hii region in an isothermal sphere, and (3) the
photo-evaporation of a dense, cold clump, similar to Test 3.  We turn
off self-gravity and AMR in accordance with RT09.

@@

We have completed presenting results from the RT06 and RT09 test
suites.  We expand on these test suites to include more complex
situations, such as a Rayleigh-Taylor problem illuminated by a
radiation source, champagne flows, an irradiated blast wave,
collimated radiation, and an \hii with a variable source that further
demonstrate its capabilities and accuracy.  Last we use the new MHD
implementation in \enzo~v2.0 in the problem of a growing \hii region
in a magnetic field.
